Golf-Sport: Managing Operations \\ A Case Study in Optimization

### 2018-05-03 Paper.tex
proof

In a survey of optimization techniques being used within operations management, the authors have broken the process into three distinct parts. These can be identified as input management, facilities management, and output management. Stated more simply, these correspond to scheduling, production, and vehicle routing, respectively. Failure to optimize any one of these areas can lead large inefficiencies (i.e. lost revenue) for a company. Making too much of one product leads to inventory costs, failure to plan good routes leads to higher shipping costs, and not spending enough on advertising leads to missed opportunities and subpar performance. Johnannesson and Karsten go on to say, ``As such problems often have a large scale, the impact can be significant. For example, it is not uncommon to be able to decrease logistics spending by 5 to 10 percent in a supply chain with annual logistics costs of over \$100 million. 

@@

Golf-Sport is a small-sized company that produces high-quality components for people who build their own golf clubs and prebuilt sets of clubs. There are five components—steel shafts, graphite shafts, forged iron heads, metal wood heads, and metal wood heads with titanium inserts—made in three plants—Chandler, Glendale, and Tucson—in the Golf-Sport system. Each plant can produce any of the components, although each plant has a different set of individual constraints and unit costs. These constraints cover labor and packaging machine time (the machine is used by all components). Note that even though the components are identical in the three plants, different production processes are used, and therefore the products use different amounts of resources in different plants.

@@

Besides component sales, the company takes the components and manufactures sets of golf clubs. Each set requires 13 shafts, 10 iron heads, and 3 wood heads. All of the shafts in a set must be the same type (steel or graphite), and all of the wood heads must be the same type (metal or metal with inserts). Each plant has unique assembly times.
Each plant of Golf-Sport has a retail outlet to sell components and sets, and the specific plant is the only supplier for its retail outlet. The minimum and maximum amounts of demand for each plant–product pair are unique. Note that, although the minimums must be satisfied, you do not need to satisfy demand up to the maximum amount.

@@

The goal is to determine a recommendation for the company. A recommendation includes a plan for production and sales. Additionally, the following sensitivity-analysis issues were explored:

@@

	\item 	Marketing is trying to get Golf-Sport to consider an advertising program that promises a 50\% increase in their maximum demand. Can the 		current system be utilized to increase profit with this new scheme?

@@

a modeling need for a third month, this could be accomplished by expanding the current model. \par
The second assumption used is the carryover of graphite stock between months.  Advertising and graphite allotments are companywide in this problem, and 
it is clearly stated that the amount of money earmarked for advertising each month will not carryover into the next month.  Graphite has no such restriction, so 

@@

\textit{x} & Production of Product \textit{i} in Period \textit{j} \\

@@

Constraints 1-4 represent the labor and packing limitations by plant with cost by product.  The first month's costs include the items manufactured and sold that month, as well as the items manufactured 
for carryover into the second month.  Constraints 5-8 represent the global constraints in this problem:  advertising budget and graphite stock.  The advertising budget is a fixed amount for each month, with no carryover. The 
graphite stock has a consistent amount per month as well, but excess from the first month can be carried over into the next month.  This carryover amount is represented by \textit{e}.  Constraints 9 \& 10 represent the unique assembly time 
for the sets of clubs, again varying by plant location. 
\par
The final constraints (11-14) represent variable bounds.  Constraint 11 ensures that all items produced and sold in period 1 are within the minimum and maximum demand.  Similarly, inequality 12 ensures that the sum of items produced in period 2 and items carryed over to 
period 2 are within that month's demand bounds.  Constraints 13 \& 14 further bound all items to be non-negative.

@@

First, while the original analysis and model does maximize profit, the actual production plan does not appear very practical for a business.  
For example, the existing parameters seem to not account for maintaining a workforce and the minimum demand is set too low to stock the shelves of a retail outlet.  This analysis will adjust some of these parameters and constraints to produce a more 

@@

$$ mz_{j} >= \sum_{i} x_{j}, z\in {0,1} $$

@@

$$f(x) = \sum_{j=1}^{3}Rx_{i} - \sum_{j=1}^{3}Cx_{i} - \sum Ix_{i,3} -\sum Sz_{j}$$

@@

Range sensitivity and resource increases were examined in regards to this problem.  The two main points of focus (as supplied by the case study) are a hypothetical increase in total maximum demand and proposed increases in advertising or graphite budget.  Both of these situations 
will be examined independently, using the initial mathematical model as the basis.

@@

as it will not increase profit beyond this point.

@@

\section{Conclusions \& Implications}
\subsection{Mathematical Approach}
Mathematically speaking, the Golf-Sport case study was successfully modeled, coded, and solved.  Depending on the setup of the code, each run took between 13 seconds and 30 minutes for completion.  When the problem was modeled as a linear relaxation, solutions took seconds to be produced.  Solutions were effectively produced and passed spot testing on various constraints in an attempt to verify solution integrity.
\par
Critically viewed, the model was effective but perhaps inefficient, especially if extended beyond the two-month period under analysis.  From a retrospective viewpoint, the model could possibly have been developed with the variables as ``produced" and ``sold", eliminating the need for the ambiguous Period 3 connotation.  A model developed in this sense could be easily expanded to more subsequent periods, increasing its utility to the organization.  It should be noted that these possible adjustments, however, would not produce any different results than what has been achieved in the current model.  An example of such a modifed objective function could be:
$$ f(x) = \sum Rs_{i,j} - \sum Cp_{i,j} - \sum I(p_{i,j}-s_{i,j}) $$
This function sets \textit{S} and \textit{P} as sold and produced items, with the difference between the two per period being the carryover inventory.
\par
In summary, the mathematical formulation and application on the Golf-Sport case study can be viewed as successful and easily modified to evaluate different parameters and constraints.
\subsection{Company Approach}
Upon completion of this analysis, it is evident that Golf-Sport can easily maximize their profit by utlizing such a model.  The parameters included, however, are superficial and unrealistic in many cases.  The problem modification above adjusts some constraints and adds to others, so as to help illustrate the process of developing a more complete picture of Golf-Sport operations.  While the actual numbers in the formulation are either arbitrary or unique to this case study, the modeling method utilized could be expanded and modified to fit many other production situations.

>>>>

In a survey of optimization techniques being used within operations management, the authors have broken the realm into three distinct sectors. These can be identified as input management, facilities management, and output management. Stated more simply, these correspond to scheduling, production, and vehicle routing. Failure to optimize any one of these areas can lead large inefficiencies (i.e. lost revenue) for a company. Making too much of one product leads to inventory costs, failure to plan good routes leads to higher shipping costs, and not spending enough on advertising leads to missed opportunities and subpar performance. Johnannesson and Karsten go on to say, ``As such problems often have a large scale, the impact can be significant. For example, it is not uncommon to be able to decrease logistics spending by 5 to 10 percent in a supply chain with annual logistics costs of over \$100 million. 

@@

Golf-Sport is a small-sized company that produces high-quality components for people who build their own golf clubs and prebuilt sets of clubs. There are five components:  steel shafts, graphite shafts, forged iron heads, metal wood heads, and metal wood heads with titanium inserts; these products are produced in three plants:  Chandler, Glendale, and Tucson. Each plant can produce any of the components, although each plant has a different set of individual constraints and unit costs. These constraints cover labor and packaging machine time (the machine is used by all components). Note that even though the components are identical in the three plants, different production processes are used, and therefore the products use different amounts of resources in different plants.

@@

Besides component sales, the company takes the components and manufactures sets of golf clubs. Each set requires 13 shafts, 10 iron heads, and 3 wood heads. All of the shafts in a set must be the same type (steel or graphite), and all of the wood heads must be the same type (metal or metal with inserts). Each plant has unique assembly times.  Furthermore, each plant of Golf-Sport has a retail outlet to sell components and sets, and the specific plant is the only supplier for its retail outlet. The minimum and maximum amounts of demand for each plant–product pair are unique.

@@

The goal of this optimization is to develop a production plan that will maximize profit for the company. Additionally, the following sensitivity-analysis issues will be explored:

@@

	\item Marketing is trying to get Golf-Sport to consider an advertising program that promises a 50\% increase in their maximum demand. Can the current system be utilized to increase profit with this new scheme?

@@

a modeling need for a third month, this could be accomplished by expanding the current model.
The second assumption concerns the carryover of graphite stock between months.  Advertising and graphite allotments are companywide in this problem, and 
it is clearly stated that unused money earmarked for advertising each month will not carry over into the next month.  Graphite has no such restriction, so 

@@

\textit{x} & Production/Sale of Product \textit{i} in Period \textit{j} \\

@@

Constraints 1-4 represent the labor and packing limitations by plant with cost by product.  The first month's costs include the items manufactured and sold that month, as well as the items manufactured 
for carryover into the second month.  Constraints 5-8 represent the global constraints in this problem:  advertising budget and graphite stock.  The advertising budget is a fixed amount for each month, with no carryover. The 
graphite stock has a consistent amount per month as well, but excess from the first month can be carried over into the next month.  This carryover amount is represented by \textit{e}.  Constraints 9 and 10 represent the unique assembly time 
for the sets of clubs, again varying by plant location. 
\par
The final constraints (11-14) represent variable bounds.  Constraint 11 ensures that all items produced and sold in period 1 are within the minimum and maximum demand.  Similarly, inequality 12 ensures that the sum of items produced in period 2 and items carried over to 
period 2 are within that month's demand bounds.  Constraints 13 and 14 further bound all items to be non-negative.

@@

First, while the original analysis and model does maximize profit, the actual production plan does not appear completely practical for a business recommendation.  For example, the existing parameters seem to not account for maintaining a workforce, and the minimum demand is set too low to stock the shelves of a retail outlet.  This analysis will adjust some of these parameters and constraints to produce a more 

@@

$$ mq_{j} >= \sum_{i} x_{j}, q\in {0,1} $$

@@

$$f(x) = \sum_{j=1}^{3}Rx_{i} - \sum_{j=1}^{3}Cx_{i} - \sum Ix_{i,3} -\sum Sq_{j}$$

@@

Range sensitivity and resource increases were examined in regards to this problem.  The two main points of focus are a hypothetical increase in total maximum demand and proposed increases in advertising or graphite budget.  Both of these situations 
will be examined independently, using the initial mathematical model (not the modified model from the prior section) as the basis.

@@

as it will not directly increase profit beyond this point.

@@

\section{Conclusions \& Implications}
\subsection{Mathematical Approach}
Mathematically speaking, the Golf-Sport case study was successfully modeled, coded, and solved.  Depending on the setup of the code, each run took between 13 seconds and 30 minutes for completion.  When the problem was modeled as a linear relaxation, solutions took seconds to be produced.  Solutions were effectively produced and passed spot testing on various constraints in an attempt to verify solution integrity.
\par
Critically viewed, the model was effective but perhaps inefficient, especially if extended beyond the two-month period under analysis.  From a retrospective viewpoint, the model could possibly have been developed with the variables as ``produced" and ``sold", eliminating the need for the ambiguous Period 3 connotation.  A model developed in this sense could be more easily expanded to more subsequent periods, increasing its utility to the organization.  It should be noted that these possible adjustments, however, would not produce any different results than what has been achieved in the current model.  An example of such a modifed objective function could be:
$$ f(x) = \sum Rs_{i,j} - \sum Cp_{i,j} - \sum I(p_{i,j}-s_{i,j}) $$
This function sets \textit{S} and \textit{P} as sold and produced items, with the difference between the two per period being the carryover inventory.
\par
In summary, the mathematical formulation and application on the Golf-Sport case study can be viewed as successful and easily modified to evaluate different parameters and constraints.
\subsection{Company Approach}
Upon completion of this analysis, it is evident that Golf-Sport can easily maximize their profit by utlizing such a model.  The parameters included, however, are superficial and unrealistic in many cases.  The problem modification above adjusts some constraints and adds to others, so as to help illustrate the process of developing a more complete picture of Golf-Sport operations.  While the actual numbers in the formulation are either arbitrary or unique to this case study, the modeling method utilized could be expanded and modified to fit many other production situations.
